\chapter{\MakeUppercase{Technical Specification}}
\section{Requirements}
\subsection{Functional Requirements}
QNA-Auth will meet the following functional requirements: 
\begin{itemize}
	\item the ability to enroll a device by capturing noise samples via the camera or microphone.
	\item the ability to create and store device templates for future verification.
	\item the ability to verify a device that has been verified with new noise samples.
	\item the ability to create and execute a two-step challenge/verification.
	\item the ability to view, manage, and delete enrolled devices.
	\item and the ability to log verification requests and audit log entries into your database.
\end{itemize}

\subsection{Non-Functional Requirements}
Reproducibility, modularity, explainability, and review-day stability are non-functional requirements that are critical; the repository supports these requirements through centralized configuration, a shared feature pipeline, runtime counters, diagnostic scripts, and fallback demo documentation. In the thesis context, results that are not reproducible or explainable have limited academic value, therefore these issues need to be taken seriously.

\subsection{Software and Hardware Requirements}
The software requirements to run the system include: Python, FastAPI, PyTorch, NumPy, SciPy, SQLAlchemy, SQLite, React, Vite. The hardware requirements are low; just a system capable of running both the backend and frontend along with an optional camera and microphone to collect data live. If live hardware is unstable, pre-recorded client samples may be provided via the API for demonstration.

\section{Feasibility Study}
Because of how feature extraction functions over a 1D array and how light the embedding model is, this project is possible from a technical perspective. In addition, the backend can support CPU execution (if GPU inference is not available).The system is operationally feasible for a capstone project because it contains demo-mode configuration, preflight diagnostic scripts, and artifact-based fallback procedures.

From a research standpoint, it has been confirmed that the research feasibility is positive but limited. The codebase already has multiple evaluation modes, sweepable thresholds and attack summary modes; however, due to the dataset size limitations, it has not yet been fully proven that the system is possible in research as a prototype only (i.e., no final production-level conclusion).

\section{System Specification}
The project uses a layered architecture. Table \ref{tab:specstack} summarizes the core technical specification.

\begin{table}[h!]
	\centering
	\caption{System specification summary}
	\renewcommand{\arraystretch}{1.3}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Component} & \textbf{Technology} & \textbf{Role} \\
		\hline
		Backend & FastAPI + Pydantic & REST API and request validation \\
		Model & PyTorch & Embedding network and similarity scoring \\
		Preprocessing & NumPy + SciPy & Feature extraction from noise arrays \\
		Database & SQLite + SQLAlchemy & Persistent devices, challenges, and logs \\
		Frontend & React + TypeScript & User-facing controls for demo and review \\
		Reporting & Python scripts & Evaluation summaries and review brief generation \\
		\hline
	\end{tabular}
\label{tab:specstack}
\end{table}

\section{Feature Pipeline Specification}
The canonical feature pipeline in \texttt{preprocessing/features.py} The implementation of shared features across multiple usage contexts, e.g. training, evaluation, or run-time (serving), is critical to the design of a similarity system due to the fact that having different sets of features between training and serving is one of the simple ways to invalidate a similarity system’s usefulness.

Each sample is converted into a fixed-dimensional representation consisting of:
\begin{itemize}
	\item raw-domain statistical features such as mean, standard deviation, range, quartiles, \ac{rms}, and peak factor,
	\item entropy measures,
	\item normalized-domain spectral features such as centroid, spread, flatness, and band powers,
	\item autocorrelation-derived descriptors,
	\item complexity measures such as approximate entropy and Hurst exponent.
\end{itemize}

If $x$ is an extracted feature vector, the learned embedding is defined by:
\begin{equation}
e = \frac{f_{\ac{theta}}(x)}{\left\|f_{\ac{theta}}(x)\right\|_2}
\end{equation}
and cosine similarity is used for comparison:
\begin{equation}
s(e_i,e_j) = \frac{e_i \cdot e_j}{\|e_i\|_2 \|e_j\|_2}
\end{equation}

\section{Decision Threshold Specification}
Runtime decisions rely on confidence bands rather than a single binary threshold. The active configuration sets:
\begin{equation}
\ac{tauS} = 0.97,\hspace{1cm}\ac{tauU} = 0.92
\end{equation}
This means:
\begin{itemize}
	\item similarity $\geq \ac{tauS}$ implies strong accept,
	\item similarity between $\ac{tauU}$ and $\ac{tauS}$ implies uncertain,
	\item similarity $< \ac{tauU}$ implies reject.
\end{itemize}

The system also uses an identification margin:
\begin{equation}
s_{claimed} - s_{best\_other} \geq \ac{margin}
\end{equation}
where the configured margin is 0.02. This reduces the chance of accepting a claimed device when an impostor score is nearly as high.

\section{Security Controls}
The principal security measures contained within this implementation include:
\begin{itemize}
	\item Nonce bound challenge generation with short expiration,
	\item \ac{hkdf} derived MAC keys bound to a combination of stable feature bytes, nonce, and server secret,
	\item Optional enforcement of an API Key,
	\item Rate limiting by IP address,
	\item Challenge persistence through database storage,
	\item Audit logging of enrollment, authentication, verification, and deletion.
\end{itemize}

These controls do not make the system invulnerable, but they do meaningfully improve the quality of the implementation relative to a purely academic scoring script.
